---
title: "Deshka Weir 2018 - coho"
author: "Adam Reimer"
date: "January 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(aslpack)
knitr::opts_chunk$set(echo = FALSE)
coho_weir <- 
  readxl::read_xlsx(".\\2018 Deshka coho sex comp_DL.xlsx",
                    sheet = 3,
                    range = "A5:F48",
                    col_names = c("date", "passage", "samples", "strata"),
                    col_types = c("date", "numeric", rep("skip", 2), "numeric", "text"))
#extend second and last strata to encoumpass all earlier (and later) weir counts
coho_weir$strata <- ifelse(coho_weir$date < as.POSIXct("2018-07-23 UTC"), 2, coho_weir$strata)
coho_weir$strata <- ifelse(coho_weir$date > as.POSIXct("2018-08-26 UTC"), 6, coho_weir$strata)

coho_weir_strata <-
  coho_weir %>%
  dplyr::group_by(strata) %>%
  dplyr::summarise(total = sum(passage),
                   samples = sum(samples))
coho_weir_sum <- dplyr::summarise(coho_weir_strata, total = sum (total))

coho_sl <- 
  readxl::read_xlsx(".\\2018 Deshka coho sex comp_DL.xlsx",
                    sheet = 2,
                    range = "A3:F302",
                    col_names = c("date", "sex", "length", "strata"),
                    col_types = c("date", rep("skip", 2), "text", "numeric", "text"))
biglg <- coho_sl$length[coho_sl$length >700]
coho_sl$sex <- toupper(coho_sl$sex)

```
  
## Coho SL
Note there were `r length(biglg)` records with lengths of `r biglg[1]` and `r biglg[2]`.  I dropped the last digit in both cases, let me know if that is incorrect.
```{r}
coho_sl$length[coho_sl$length == 5758] <- 575
coho_sl$length[coho_sl$length == 4954] <- 495
```

Sex composition of coho salmon does not differ between time strata, indicating pooled ASL estimates are sufficient. I also ran the stratified estimate but the pooled estimate had nearly identical point estimates with smaller SE's.
```{r}
#sex comp time invariant
tab_lr(coho_sl, "sex")
```

Here is the pooled coho sex-length table. We met the precision objective.
```{r}
pooled_sl <- asl(coho_sl, coho_weir_sum) %>%
  tab_asl(totalname = "Weir Passage", output = "sl")
knitr::kable(pooled_sl)
```

```{r}
WriteXLS::WriteXLS("pooled_sl",
                   ".\\18 Deshka coho SL.xlsx",
                   SheetNames = c("coho sex comp"),
                   AdjWidth = TRUE,
                   BoldHeaderRow = TRUE)
```
