---
title: "Deshka Weir 2018 - Chinook"
author: "Adam Reimer"
date: "October 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(aslpack)
knitr::opts_chunk$set(echo = FALSE)
weir <- readxl::read_xlsx(".\\2018 Deshka Chinook Age Analysis_DL.xlsx",
                         sheet = 2,
                         range = "A11:M102",
                         col_names = c("date", "passage", "samples", "strata"),
                         col_types = c("date", "numeric", rep("skip", 3), "guess", rep("skip", 6), "numeric"))
weir_sum <- data.frame(total = sum(weir$passage))

asl_dat <- readxl::read_xlsx(".\\2018 Deshka Chinook Age Analysis_DL.xlsx",
                          sheet = 4,
                          range = "A5:J248",
                          col_names = c("date", "sex", "length", "age", "strata"),
                          col_types = c("date", rep("skip", 2), rep("guess", 2), rep("skip", 3), "text", "numeric"))
asl_dat$age[grepl("1.1", asl_dat$age)] <- 1.1
```

## Chinook ASL
I redefined the strata assignments so that ASL and weir assignments matched and so approximately 25% of the passaged occurred in each stratum.
```{r}
breaks <- c(as.POSIXct("2018-05-1 UTC"),
            as.POSIXct("2018-06-16 UTC"),
            as.POSIXct("2018-06-21 UTC"),
            as.POSIXct("2018-06-25 UTC"),
            as.POSIXct("2018-08-31 UTC"))
weir$strata <- cut(weir$date, breaks, labels = 1:4)
asl_dat$strata <- cut(asl_dat$date, breaks, labels = 1:4)
compare_strata(asl_dat, weir, passage)[, c("strata", "asl_dates", "asl_pct", "total_dates", "total_pct")]
```
 ASL samples were not collected in proportion to abundance indicating a need to stratify composition estimates provided they differ between stratum.
```{r, , fig.width = 10, fig.height = 8}
plot_ks(weir, "passage")
```

### Chinook sex composition
Likelihood ratio tests indicate sex composition was similar between time strata, which is evidence we don't need to stratify.
```{r}
t.sex<-table(asl_dat$strata,asl_dat$sex)
addmargins(t.sex, c(1, 2))
DescTools::GTest(t.sex)
```

Here is the Chinook sex-length table. We met the precision objective.
```{r}
sl <- asl(asl_dat, weir_sum) %>% tab_asl(totalname = "Weir Passage", output = "sl", display_cols = "stat")
knitr::kable(sl)
```

### Chinook age composition
Likelihood ratio tests indicate age composition was similar between time strata, which is evidence we don't need to stratify.
```{r}
clean_age <- asl_dat[asl_dat$age %in% c("1.1", "1.2", "1.3", "1.4"), ]
t.age<-table(clean_age$strata,clean_age$age)
addmargins(t.age, c(1, 2))
DescTools::GTest(t.age)
```

Here is the Chinook age-length table. We met the precision objective.
```{r}
al <- asl(clean_age, weir_sum) %>% tab_asl(totalname = "Weir", output = "al", display_cols = "stat")
knitr::kable(al)
```

### Chinook age-sex composition
Here is the Chinook age-sex-length table.
```{r}
asl <- asl(clean_age, weir_sum) %>% tab_asl(totalname = "Weir", output = "asl")
knitr::kable(asl)
```

I've included an excel file with all of these age comps.
```{r}
WriteXLS::WriteXLS(c("sl", "al", "asl"),
                   ".\\18 Deshka ASL.xlsx",
                   SheetNames = c("Chinook sex comp", "Chinook age Comp", "Chinook agesex comp"),
                   AdjWidth = TRUE,
                   BoldHeaderRow = TRUE)
```
