---
title: "Deshka Weir 2019 - Chinook"
author: "Adam Reimer"
date: "November 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(aslpack)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
weir <- readxl::read_xlsx(".\\Copy of 2019 Deshka Chinook Age Analysis_DL_AR.xlsx",
                         sheet = 2,
                         range = "A11:M123",
                         col_names = c("date", "passage", "samples", "strata"),
                         col_types = c("date", "numeric", rep("skip", 3), "guess", rep("skip", 6), "numeric"))
weir_sum <- data.frame(total = sum(weir$passage))

#had to correct dat format in C192:194
asl_dat <- readxl::read_xlsx(".\\Copy of 2019 Deshka Chinook Age Analysis_DL_AR.xlsx",
                          sheet = 4,
                          range = "C2:K272",
                          col_names = c("date", "length", "sex", "age", "strata"),
                          col_types = c("date", rep("skip", 2), rep("guess", 2), rep("skip", 2), "text", "numeric"))
asl_dat$age[grepl("1.1", asl_dat$age)] <- 1.1
```

## Chinook ASL
The strata you assigned look good. Each strata represents about a quarter of the samples and/or escapement.
```{r}
knitr::kable(compare_strata(asl_dat, weir, passage)[, c("strata", "asl_dates", "asl_pct", "total_dates", "total_pct")], 
             col.names = c("strata", "asl_dates", "asl_pct", "escapement_dates", "escapement_pct"))
```
  
ASL samples were not collected in proportion to abundance (the sampling actually looks pretty good to me, but we fail the test). This is only a problem if the composition estimates differ between strata, so we will test for that next.
```{r, , fig.width = 7, fig.height = 7}
plot_ks(weir, "passage")
```

### Chinook sex composition
Likelihood ratio tests indicate sex composition was similar between time strata, which is evidence we don't need to stratify.
```{r}
t.sex<-table(asl_dat$strata,asl_dat$sex)
addmargins(t.sex, c(1, 2))
DescTools::GTest(t.sex)
```

Here is the Chinook sex-length table. We met the precision objective.
```{r}
sl <- asl(asl_dat, weir_sum) %>% tab_asl(totalname = "Weir Passage", output = "sl", display_cols = "stat")
knitr::kable(sl)
```

### Chinook age composition
Likelihood ratio tests indicate age composition was similar between time strata, which is evidence we don't need to stratify. I didn't include age 1.4 fish in the test because they were so infrequent but we will include them in the estimation.
```{r}
clean_age <- asl_dat[asl_dat$age %in% c("1.1", "1.2", "1.3", "1.4"), ]
#t.age<-table(clean_age$strata,clean_age$age)
#addmargins(t.age, c(1, 2))
#chisq.test(t.age)
#DescTools::GTest(t.age)

red_age <- clean_age[clean_age$age %in% c("1.1", "1.2", "1.3"), ]
t.age2<-table(red_age$strata,red_age$age)
addmargins(t.age2, c(1, 2))
#chisq.test(t.age2)
DescTools::GTest(t.age2)
```

Here is the Chinook age-length table. We met the precision objective.
```{r}
al0 <- asl(clean_age, weir_sum)
al<- al0 %>% tab_asl(totalname = "Weir", output = "al", display_cols = "stat")
knitr::kable(al)
```

### Chinook age-sex composition
Here is the Chinook age-sex-length table.
```{r}
asl <- al0 %>% tab_asl(totalname = "Weir", output = "asl")
knitr::kable(asl)
```

I've included an excel file with all of these age comps.
```{r}
WriteXLS::WriteXLS(c("sl", "al", "asl"),
                   ".\\19 Deshka ASL.xlsx",
                   SheetNames = c("Chinook sex comp", "Chinook age Comp", "Chinook agesex comp"),
                   AdjWidth = TRUE,
                   BoldHeaderRow = TRUE)
```
