---
title: "Deshka Weir 2020 - coho"
author: "Adam Reimer"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(magrittr)
source("H:\\My Documents\\R_functions\\ASL_funs.R")
coho_weir <- 
  readxl::read_xlsx(".\\2020 Deshka coho sex comp_DL.xlsx",
                    sheet = 3,
                    range = "A5:F32",
                    col_names = c("date", "passage", "samples", "strata"),
                    col_types = c("date", "numeric", rep("skip", 2), "numeric", "text"))

coho_weir_strata <-
  coho_weir %>%
  dplyr::group_by(strata) %>%
  dplyr::summarise(total = sum(passage),
                   samples = sum(samples))
coho_weir_sum <- dplyr::summarise(coho_weir_strata, total = sum (total))

coho_sl <- 
  readxl::read_xlsx(".\\2020 Deshka coho sex comp_DL.xlsx",
                    sheet = 4,
                    range = "A5:F183",
                    col_names = c("date", "sex", "length", "strata"),
                    col_types = c("date", rep("skip", 2), "text", "numeric", "text"))
coho_sl <- coho_sl[!is.na(coho_sl$sex), ] #drop fish that wasnt sampled
```
  
## Coho SL
Coho salmon sampling was insufficient to produce an unbiased estimate of sex composition or escapement by sex. Two problems were noted. First, sampling at the weir ended while significant number of fish were still migrating. I don't recall if there is a definitive pull criteria on for Deshka but I know <1% of the cumulative count for 3 days in a row is used on other projects. We should think about adding some sort of pull criteria to the next op plan. 

```{r}
#Looks like Weir was pulled early
library(ggplot2)
ggplot(coho_weir, aes(x = date, weight = passage)) + 
  geom_bar() +
  ggtitle("Deshka Coho Escapement") +
  labs(x = "Date", y = "Coho Salmon")
```

Second, fish were only sampled during 2 of 4 weekly strata, with insufficent numbers sampled in the 4th weekly strata.

```{r}
#Only 4 strata
#No samples in first 2 strata
aggregate(samples ~ strata, data = coho_weir, sum)
```

I've created a sex composition table (without apportioning the incomplete weir count for your reference. If these numbers are reported we would want to make clear it was a grab sample which may not be representative of the entire run.
```{r}
#Produced a pooled age comp without apportioning the run becasue:
#1) the weir was pulled early and
#2) the run was sampled for just a few days
pooled_sl <- asl(coho_sl) %>%
  tab_asl(totalname = "Weir Passage", output = "sl")
knitr::kable(pooled_sl)
```

The attached file has the results in excel format.
```{r}
WriteXLS::WriteXLS("pooled_sl",
                   ".\\20 Deshka coho SL.xlsx",
                   SheetNames = c("coho sex comp"),
                   AdjWidth = TRUE,
                   BoldHeaderRow = TRUE)
```
