---
title: "Deshka Weir 2022 - Chinook"
author: "Logan Wendling"
date: '2022-11-02'
output: html_document
---

```{r,echo=F,warning=FALSE,message=FALSE}
setwd("S:/RTS/DeshkaWeir/2022")
library(lubridate)
library(WriteXLS)
```

```{r setup, include=FALSE}
source("H:\\My Documents\\R_functions\\ASL_funs.R")
library(magrittr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
weir <- readxl::read_xlsx(".\\Deshka Chinook Age Analysis 2022_DL.xlsx",
                          sheet = 2,
                          range = "A11:M80",
                          col_names = c("date", "passage", "samples", "strata"),
                          col_types = c("date", "numeric", rep("skip", 3), "guess", rep("skip", 6), "numeric"))

asl_dat <- readxl::read_xlsx(".\\Deshka Chinook Age Analysis 2022_DL.xlsx",
                             sheet = 4,
                             range = "D2:N130",
                             col_names = c("date", "length", "sex", "age", "strata"),
                             col_types = c("date", rep("skip", 2), rep("guess", 2), rep("skip", 4), "text", "numeric"))
asl_dat$age[grepl("1.1", asl_dat$age)] <- 1.1


strat1 <- interval(ymd("2022-05-31 UTC"),ymd("2022-06-18 UTC"))   #Adjust Begin and end dates for strata
strat2 <- interval(ymd("2022-06-19 UTC"),ymd("2022-06-28 UTC"))
strat3 <- interval(ymd("2022-06-29 UTC"),ymd("2022-08-08 UTC"))
#strat4 <- interval(ymd(NA),ymd(NA))

asl_dat$strata <- ifelse( asl_dat$date %within% strat1,1,asl_dat$strata)   #Assign strata to dates
asl_dat$strata <- ifelse( asl_dat$date %within% strat2,2,asl_dat$strata)
asl_dat$strata <- ifelse( asl_dat$date %within% strat3,3,asl_dat$strata)
#asl_dat$strata <- ifelse( asl_dat$date %within% strat4,4,asl_dat$strata)   

weir$strata <- ifelse( weir$date %within% strat1,1,weir$strata)   #Assign strata to dates to match ASL
weir$strata <- ifelse( weir$date %within% strat2,2,weir$strata)
weir$strata <- ifelse( weir$date %within% strat3,3,weir$strata)
weir$strata <- ifelse( weir$date %within% strat3,3,weir$strata)

weir_strata <- 
  weir %>%
  dplyr::group_by(strata) %>%
  dplyr::summarise(total = sum(passage))
weir_sum <- data.frame(total = sum(weir$passage))
```


## Chinook ASL


```{r}
knitr::kable(compare_strata(asl_dat, weir, passage)[, c("strata", "asl_dates", "asl_pct", "total_dates", "total_pct")], 
             col.names = c("strata", "asl_dates", "asl_pct", "escapement_dates", "escapement_pct"))
```



```{r, , fig.width = 7, fig.height = 7}
plot_ks(weir, "passage")
```

### Chinook sex composition

Likelihood ratio tests indicate sex composition did not differ between time strata.

```{r}
t.sex<-table(asl_dat$strata,asl_dat$sex)
addmargins(t.sex, c(1, 2))
DescTools::GTest(t.sex)
```

Here is the Chinook sex-length table. We used a time stratified estimate and met the precision objective.

```{r}
sl <- 
  asl(asl_dat, weir_strata, groupvars = "strata") %>% 
  combine_strata() %>% 
  tab_asl(totalname = "Weir Passage", output = "sl", display_cols = "stat")
knitr::kable(sl)
```

### Chinook age composition

Likelihood ratio tests indicate age composition differed between time strata.

```{r}
clean_age <- asl_dat[asl_dat$age %in% c("1.1", "1.2", "1.3", "1.4"), ]
t.age <- table(clean_age$strata,clean_age$age)
addmargins(t.age, c(1, 2))
DescTools::GTest(t.age)
```

Here is the Chinook age-length table. We used a time stratified estimate and met the precision objective.

```{r}
al0 <- asl(clean_age, weir_strata, groupvars = "strata")
al<- 
  al0 %>% 
  combine_strata() %>%
  tab_asl(totalname = "Weir", output = "al", display_cols = "stat")
knitr::kable(al)
```

### Chinook age-sex composition

Here is the Chinook age-sex-length table.

```{r}
chin_asl <- 
  al0 %>%
  combine_strata() %>% 
  tab_asl(totalname = "Weir", output = "asl") 
knitr::kable(chin_asl)
```

I've included an excel file with all of these age comps.

```{r,warning=FALSE}
library(openxlsx)
#WriteXLS(x = c("sl", "al", "chin_asl"),ExcelFileName = ".//22 Deshka ASL_LFW10_4.xlsx",
#                   SheetNames = c("Chinook sex comp", "Chinook age Comp", "Chinook agesex comp"),
#                   AdjWidth = TRUE,
 #                  BoldHeaderRow = TRUE,envir = parent.frame())

WB = createWorkbook("Deshka ASL")
addWorksheet(WB,"Chinook Sex Comp")
addWorksheet(WB,"Chinook Age Comp")
addWorksheet(WB,"Chinook SexAge Comp")
writeData(WB,sheet = 1,sl,colNames = TRUE)
writeData(WB,sheet = 2,al,colNames = TRUE)
writeData(WB,sheet = 3,chin_asl,colNames = TRUE)
saveWorkbook(WB, ".//22 Deshka ASL_LFW10_4.xlsx", overwrite = TRUE)


#write.xlsx(sl,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook Sex Comp",colNames = TRUE)
#write.xlsx(al,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook Age Comp",append = TRUE)
#write.xlsx(chin_asl,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook AgeSex Comp",append = TRUE)

```


