---
title: "Deshka Weir 2021 - Chinook"
author: "Adam Reimer"
date: "December 1, 2021"
output: html_document
---

```{r setup, include=FALSE}
source("H:\\My Documents\\R_functions\\ASL_funs.R")
library(magrittr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
weir <- readxl::read_xlsx(".\\Deshka Chinook Age Analysis 2021_DL.xlsx",
                          sheet = 2,
                          range = "A11:M94",
                          col_names = c("date", "passage", "samples", "strata"),
                          col_types = c("date", "numeric", rep("skip", 3), "guess", rep("skip", 6), "numeric"))

asl_dat <- readxl::read_xlsx(".\\Deshka Chinook Age Analysis 2021_DL.xlsx",
                             sheet = 4,
                             range = "D2:O371",
                             col_names = c("date", "length", "sex", "age", "strata"),
                             col_types = c("date", rep("skip", 2), rep("guess", 2), rep("skip", 5), "text", "numeric"))
asl_dat$age[grepl("1.1", asl_dat$age)] <- 1.1

asl_dat$strata <- ifelse(asl_dat$strata == 1 & asl_dat$date >= as.POSIXct("2021-06-9 UTC"), 2, asl_dat$strata)
asl_dat$strata <- ifelse(asl_dat$strata == 4 & asl_dat$date <= as.POSIXct("2021-06-22 UTC"), 3, asl_dat$strata)
weir$strata <- ifelse(weir$strata == 1 & weir$date >= as.POSIXct("2021-06-9 UTC"), 2, weir$strata)
weir$strata <- ifelse(weir$strata == 4 & weir$date <= as.POSIXct("2021-06-22 UTC"), 3, weir$strata)

weir_strata <- 
  weir %>%
  dplyr::group_by(strata) %>%
  dplyr::summarise(total = sum(passage))
weir_sum <- data.frame(total = sum(weir$passage))
```

## Chinook ASL
I made slight adjustments to the time strata so that the sex composition was more homogeneous withing each strata.
```{r}
knitr::kable(compare_strata(asl_dat, weir, passage)[, c("strata", "asl_dates", "asl_pct", "total_dates", "total_pct")], 
             col.names = c("strata", "asl_dates", "asl_pct", "escapement_dates", "escapement_pct"))
```
  
ASL samples were not collected in proportion to abundance. If the sex and age compositions also differ by strata it would make sense to use a stratified estimate.  
```{r, , fig.width = 7, fig.height = 7}
plot_ks(weir, "passage")
```

### Chinook sex composition
Likelihood ratio tests indicate sex composition differed between time strata.
```{r}
t.sex<-table(asl_dat$strata,asl_dat$sex)
addmargins(t.sex, c(1, 2))
DescTools::GTest(t.sex)
```

Here is the Chinook sex-length table. We used a time stratified estimate and met the precision objective.
```{r}
sl <- 
  asl(asl_dat, weir_strata, groupvars = "strata") %>% 
  combine_strata() %>% 
  tab_asl(totalname = "Weir Passage", output = "sl", display_cols = "stat")
knitr::kable(sl)
```

### Chinook age composition
Likelihood ratio tests indicate age composition differed between time strata.
```{r}
clean_age <- asl_dat[asl_dat$age %in% c("1.1", "1.2", "1.3", "1.4"), ]
t.age<-table(clean_age$strata,clean_age$age)
addmargins(t.age, c(1, 2))
DescTools::GTest(t.age)
```

Here is the Chinook age-length table. We used a time stratified estimate and met the precision objective.
```{r}
al0 <- asl(clean_age, weir_strata, groupvars = "strata")
al<- 
  al0 %>% 
  combine_strata() %>%
  tab_asl(totalname = "Weir", output = "al", display_cols = "stat")
knitr::kable(al)
```

### Chinook age-sex composition
Here is the Chinook age-sex-length table.
```{r}
chin_asl <- 
  al0 %>%
  combine_strata() %>% 
  tab_asl(totalname = "Weir", output = "asl") 
knitr::kable(chin_asl)
```

I've included an excel file with all of these age comps.
```{r}
WriteXLS::WriteXLS(c("sl", "al", "chin_asl"),
                   ".\\21 Deshka ASL.xlsx",
                   SheetNames = c("Chinook sex comp", "Chinook age Comp", "Chinook agesex comp"),
                   AdjWidth = TRUE,
                   BoldHeaderRow = TRUE)
```